Predicting the effects of character displacement on food-web dynamics

### 2019-10-30 Appendix_S4.Rmd
finalize edits for Appendix S4 for bioRxiv submission

---
#title: |
#   | Predicting the effects of character displacement on food-web dynamics
#   | Food-web dynamics under ecological character displacement
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$
# potentially use for 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348 for cross-format compatibility, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib 
#    includes:  
#      in_header: Am-Nat-preamble-latex.tex
header-includes:
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{fullpage}
- \linespread{1.7}
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

*Elements*: Figures S1 and S2.

@@

(ignore this blank page for the moment. Rmarkdown can be a pain in the ass.)

```{r McCann_Plot, echo=FALSE, fig.pos="H", fig.cap="Figure S1: **Effect of character displacement when consumers exhibit a more realistic functional response.** Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in stability panel). This figure illustrates how, regardless of the tradeoff, character displacement increases the effective attack rate of consumers. This always resulted in a suppression of resource abundances and concomitant decrease in food-web stability. Initial parameter and state variables are given in the main text."}
knitr::include_graphics("Figure_ECD_McCann.pdf")
```

@@

```{r All asymmetric figs, echo=FALSE, fig.pos="H", fig.cap=""}
knitr::include_graphics("asymm_figs.pdf")
```

Figure S2: **Robustness to consumer asymmetry**. Scenarios correspond to: (I) resources occur in the same habitat and consumer(s) exhibits a linear functional response; (II) resources occur in different habitats and consumer(s) exhibits a linear functional response; (III) resources occur in different habitats and consumer(s) exhibits a more realistic functional response (details in main text). Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in stability panels). The similarity with fig. S1 and fig. 2 (main text) show that adding an asymmetry in consumer attack rates does not alter the conclusions reported in the main text. If anything, it is more likely that an asymmetry will push the system toward the boundary of stability (note position of large circles in stability panel of Scenario I). Details of the consumer asymmetry simulation are given in the main text.

@@

```{r McCann_Plot_asymm, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:McCann_Plot_asymm}**Effect of character displacement when consumers exhibit a more realistic functional response and have an asymmetry in initial attack rates.** Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points. Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of consumers. This always resulted in a suppression of resource abundances (B) and concomitant decrease in food-web stability (C). These simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2; *w~ii~*=0.6, *w~ij~*=0.4. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. To create an asymmetry in initial attack rates, we used the ending *a~ii~* and *a~ij~* values for the one consumer simulation as the starting values for *C~2~* in the two consumer simulation. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_McCann_asymm.pdf")
```

>>>>

---
#title: |
#   | Predicting the effects of character displacement on food-web dynamics
#   | Food-web dynamics under ecological character displacement
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$
# potentially use for 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348 for cross-format compatibility, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib 
    #includes:  
    #  in_header: Am-Nat-preamble-latex.tex
header-includes:
  - \usepackage{fullpage}
  - \linespread{1.5} 
  - \usepackage{lineno}
  - \usepackage{caption}
  - \captionsetup[figure]{font=small,labelformat=empty}
#- \usepackage{caption}
#- \captionsetup[figure]{labelformat=empty}
#- \usepackage{fullpage}
#- \linespread{1.7}
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

*Elements*: Figures S1, S2, and S3.

@@

<!--(ignore this blank page for the moment. Rmarkdown can be a pain in the ass.)-->

```{r McCann_Plot, echo=FALSE, fig.pos="H", fig.cap="Figure S1: **Effect of character displacement when consumers exhibit a more realistic functional response.** Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation for *C*~1~, whereas as small shapes correspond to the starting points (only in stability panel). This figure illustrates how, regardless of the tradeoff, character displacement increases the effective attack rate of consumers. This always resulted in a suppression of resource abundances and concomitant decrease in food-web stability. Initial parameter and state variables are given in the main text."}
knitr::include_graphics("Figure_ECD_McCann.pdf")
```

@@

```{r All asymmetric figs, echo=FALSE, fig.pos="H", fig.cap="Figure S2: **Robustness to consumer asymmetry**. Lines show predicted values when both consumers and resources are present. Different line colors correspond to different tradeoffs in attack rates (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation for *C*~1~, whereas as small shapes correspond to the starting points (only in stability panels). In both foraging scenarios, feeding rates increase linearly with resource abundance, but the equation for effective attack rate is different. The similarity with fig. 3 (main text) shows that adding an asymmetry in consumer attack rates does not alter the conclusions reported in the main text. If anything, it is more likely that an asymmetry will push the system toward the boundary of stability (note position of large circles in lower left stability panel). Details of the consumer asymmetry simulation are given in the main text."}
knitr::include_graphics("asymm_figs.pdf")
```

@@

```{r McCann_Plot_asymm, echo=FALSE, fig.cap="Figure S3: **Robustness to consumer asymmetry when consumers exhibit a more realistic functional response.** Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation for *C*~1~, whereas as small shapes correspond to the starting points. Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of consumers. This always resulted in a suppression of resource abundances (B) and concomitant decrease in food-web stability (C). The similarity with fig. S1 shows that adding an asymmetry in consumer attack rates does not alter the conclusions reported in the main text. Details of the consumer asymmetry simulation are given in the main text."}
knitr::include_graphics("Figure_ECD_McCann_asymm.pdf")
```
